Fusion Moves for Correlation Clustering

### 2014-11-02 paper/egpaper_for_review.tex
inital version of descripton of 3d models

\subsection{Real World Models}

>>>>

\subsection{Real World Models}
An example for large scale correlation clustering is 
segmentation of region adjacency graphs (RAG) for
3D closed surface segmentation of neural tissue data 
\cite{kroeger_2012_eccv}.
The energy is based on a likelihood of merging adjacent super-voxels.
Each edge has a probability to keep adjacent segments separate ($p(y_{ij} =1)$)
or to merge them ($p(y_{ij} = 0)$).
The energy function is defined as following.
\begin{align}
 J(y)  &= \sum_{ij \in E} y_{ij}\cdot \underbrace{  log\left( \frac{p(y_{ij} =0)}{p(y_{ij} =1)}\right) + log \frac{1-\beta}{\beta}  }_{w_{ij}}
\end{align}
Where $\beta$ is used as a prior.
Models of different size are included in the graphical model
benchmark of Kappes \etal ~\cite{kappes_2013_benchmark_cvpr} (???).
We use models with the cube sizes $300^3$, $450^3$, $550^3$ and $900^3$.
The number of variables varies from ??? to ???, and the number
of edges from ??? to ???.

\begin{center}
    \begin{figure}
        \begin{center}
            \begin{subfigure}[b]{0.45\linewidth}
                \includegraphics[width=1.0\linewidth]{images/-010.jpg}
            \end{subfigure}
            \quad
            \begin{subfigure}[b]{0.45\linewidth}
                \includegraphics[width=1.0\linewidth]{images/-030.jpg}
            \end{subfigure}
        \end{center}
    \caption{
        Raw FIBSEM data and correlation clustering result of the model from \cite{kroeger_2012_eccv}
    }
    \end{figure}
\end{center}
